### 2021-11-18 RebuttalTemplate.tex
Init

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[rebuttal]{cvpr}

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref,breaklinks,colorlinks,bookmarks=false]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

% If you wish to avoid re-using figure, table, and equation numbers from
% the main paper, please uncomment the following and change the numbers
% appropriately.
%\setcounter{figure}{2}
%\setcounter{table}{1}
%\setcounter{equation}{2}

% If you wish to avoid re-using reference numbers from the main paper,
% please uncomment the following and change the counter for `enumiv' to
% the number of references you have in the main paper (here, 6).
%\let\oldthebibliography=\thebibliography
%\let\oldendthebibliography=\endthebibliography
%\renewenvironment{thebibliography}[1]{%
%     \oldthebibliography{#1}%
%     \setcounter{enumiv}{6}%
%}{\oldendthebibliography}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}
\appendix

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.
Please follow the steps and style guidelines outlined below for submitting your author response.

The author rebuttal is optional and, following similar guidelines to previous CVPR conferences, is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers.
It is NOT intended to add new contributions (theorems, algorithms, experiments) that were absent in the original submission and NOT specifically requested by the reviewers.
You may optionally add a figure, graph, or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

Per a passed 2018 PAMI-TC motion, reviewers should refrain from requesting significant additional experiments for the rebuttal or penalize for lack of additional experiments.
Authors should refrain from including new experimental results in the rebuttal, especially when not specifically requested to do so by the reviewers.
Authors may include figures with illustrations or comparison tables of results reported in the submission/supplemental material or in other papers.

Just like the original submission, the rebuttal must maintain anonymity and cannot include external links that reveal the author identity or circumvent the length restriction.
The rebuttal must comply with this template (the use of sections is not required, though it is recommended to structure the rebuttal for ease of reading).

%-------------------------------------------------------------------------

\subsection{Response length}
Author responses must be no longer than 1 page in length including any references and figures.
Overlength responses will simply not be reviewed.
This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The top margin should begin 1 inch (2.54 cm) from the top edge of the page.
The bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the page.

Please number any displayed equations.
It is important for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.
Main text should be in 10-point Times, single-spaced.
Section headings should be in 10 or 12 point Times.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Figure and table captions should be 9-point Roman type as in \cref{fig:onecol}.

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response.
When referenced in the text, enclose the citation number in square brackets, for example~\cite{Alpher05}.
Where appropriate, include the name(s) of editors of referenced books.

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{0.5in} \rule{0.9\linewidth}{0pt}}
  %\includegraphics[width=0.8\linewidth]{egfigure.eps}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
   \label{fig:onecol}
\end{figure}

To avoid ambiguities, it is best if the numbering for equations, figures, tables, and references in the author response does not overlap with that in the main paper (the reviewer may wonder if you talk about \cref{fig:onecol} in the author response or in the paper).
See \LaTeX\ template for a workaround.

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
Please ensure that any point you wish to make is resolvable in a printed copy of the response.
Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your response in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it is almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2021-11-18 PaperForReview.tex
Init

% CVPR 2022 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
%\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Author Guidelines for \confName~Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
   The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section, must be no longer than eight pages in length.
The references section will not be included in the page count, and there is no limit on the length of the references section.
For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for \confName\ \confYear.}

Overlength papers will simply not be reviewed.
This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera-ready copy should not contain a ruler.
(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)

Reviewers:
note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.

\subsection{Paper ID}
Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.

\subsection{Mathematics}

Please number all of your sections and displayed equations as in these examples:
\begin{equation}
  E = m\cdot c^2
  \label{eq:important}
\end{equation}
and
\begin{equation}
  v = a\cdot t.
  \label{eq:also-important}
\end{equation}
It is important for readers to be able to refer to any particular equation.
Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
All authors will benefit from reading Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind review.
Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
That is all.
(But see below for tech reports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
it says that you are building on her work.
If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:
\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
   Why the previous paper was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
Then submit the tech report as supplemental material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
solution.
The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.
Do not write ``We show how to improve our previous work [Anonymous, 1968].
This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors.
Instead write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.
   This system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
   Ours handles it by including a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
   It displayed the following behaviours, which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
For your results, however, you should not identify yourself and should not mention your participation in the challenge.
Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
  \centering
  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}

   \caption{Example of caption.
   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
   \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a sentence-ending space.
So \eg is correct, {\em e.g.} is not.
The provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
However, use it only when there are three or more authors.
Thus, the following is correct:
   ``Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.

% Update the cvpr.cls to do the following automatically.
% For this citation style, keep multiple citations in numerical (not
% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
% \cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
  \centering
  \begin{subfigure}{0.68\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{An example of a subfigure.}
    \label{fig:short-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\linewidth}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \caption{Another example of a subfigure.}
    \label{fig:short-b}
  \end{subfigure}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}
\label{sec:formatting}

All text must be in a two-column format.
The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
The second and following pages should begin 1 inch (2.54 cm) from the top edge.
On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
high.
%
Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
The \LaTeX\ template takes care of this when used properly.

%-------------------------------------------------------------------------
\subsection{Type style and fonts}

Wherever Times is specified, Times Roman may also be used.
If neither is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE.
Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type.
This information is to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT.
Type main text in 10-point Times, single-spaced.
Do NOT use double-spacing.
All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
Make sure your text is fully justified---that is, flush left and flush right.
Please do not place any additional blank lines between paragraphs.

Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-, second-, and third-order headings.

FIRST-ORDER HEADINGS.
(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS.
(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote{This is what a footnote looks like.
It often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{Cross-references}

For the benefit of author(s) and readers, please use the
{\small\begin{verbatim}
  \cref{...}
\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
This will automatically insert the appropriate label alongside the cross-reference as in this example:
\begin{quotation}
  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
\end{quotation}
If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
{\small\begin{verbatim}
  \Cref{...}
\end{verbatim}}
command. Here is an example:
\begin{quotation}
  \Cref{fig:onecol} is also quite important.
\end{quotation}

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
When referenced in the text, enclose the citation number in square brackets, for
example~\cite{Authors14}.
Where appropriate, include page numbers and the name(s) of editors of referenced books.
When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
If you use the template as advised, this will be taken care of automatically.

\begin{table}
  \centering
  \begin{tabular}{@{}lc@{}}
    \toprule
    Method & Frobnability \\
    \midrule
    Theirs & Frumpy \\
    Yours & Frobbly \\
    Ours & Makes one's heart Frob\\
    \bottomrule
  \end{tabular}
  \caption{Results.   Ours is better.}
  \label{tab:example}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.
In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
Instead use
{\small\begin{verbatim}
  \centering
\end{verbatim}}
at the beginning of your figure.
Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.pdf}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.

If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2021-11-19 paper_writing_tips.tex
Add tables

--- 2021-11-18 PaperForReview.tex
@@
 %%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
-\usepackage[review]{cvpr}      % To produce the REVIEW version
-%\usepackage{cvpr}              % To produce the CAMERA-READY version
+%\usepackage[review]{cvpr}      % To produce the REVIEW version
+\usepackage{cvpr}              % To produce the CAMERA-READY version
 %\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
@@
 \usepackage{booktabs}
+
+% included packages
+\usepackage{makecell}
+\usepackage{colortbl}
+\usepackage{xcolor}
 
@@
 
+% For caption setup
+\captionsetup[table]{aboveskip=3pt}
+\captionsetup[table]{belowskip=2pt}
+\captionsetup[figure]{aboveskip=5pt}
+\captionsetup[figure]{belowskip=0pt}
+\captionsetup{font=small}
+
 %%%%%%%%% PAPER ID  - PLEASE UPDATE
@@
 
+% utils
+\newcommand{\correct}[1]{\textcolor{blue}{#1 \checkmark}}
+\newcommand{\wrong}[1]{\textcolor{red}{#1 $\times$}}
+
 \begin{document}
@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{\LaTeX\ Author Guidelines for \confName~Proceedings}
+\title{LaTex Paper Writing Tips for Beginners}
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Guanying Chen \\
+{\tt\small guanying2018@gmail.com}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
 }
 \maketitle
+{
+    \hypersetup{linkcolor=black}
+    \tableofcontents
+}
 
 %%%%%%%%% ABSTRACT
-\begin{abstract}
-   The ABSTRACT is to be in fully justified italicized text, at the top of the left-hand column, below the author and affiliation information.
-   Use the word ``Abstract'' as the title, in 12-point Times, boldface type, centered relative to the column, initially capitalized.
-   The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
-\end{abstract}
 
 %%%%%%%%% BODY TEXT
+\vspace{6em}
 \section{Introduction}
@@
 
-Please follow the steps outlined below when submitting your manuscript to the IEEE Computer Society Press.
-This style guide now has several important modifications (for example, you are no longer warned against the use of sticky tape to attach your artwork to the paper), so all authors should read this new version.
+\section{Common Mistakes}
+\begin{itemize}
+    \item There should be a space before the open parentheses: [\wrong{hello(word)}, \correct{hello (word)}].
+    \item citation
+    \item There should be no space before the punctuation (\eg, ,. ').
+    \item \ie, \eg
+    \item Do not add citations in the abstract
+    \item Every equation should end with a punctuation.
+    \item The first character should be capitalized
+    \item keep the same tense
+    \item
+    \item
+    \item
+    \item
+    \item
+    \item
+    \item
+\end{itemize}
 
-%-------------------------------------------------------------------------
-\subsection{Language}
+\section{Suggestions}
+\begin{itemize}
+    \item use newcommand for abbr
+    \item Fig/Tab.
+    \item use newcommand in equation
+    \item Principal: be compact and clear.
+    \item Contributions
+\end{itemize}
 
-All manuscripts must be in English.
+\clearpage
+\section{Sample layout for figures}
+\begin{itemize}
+    \item The caption should be at the bottom of the figure. 
+\end{itemize}
 
-\subsection{Dual submission}
+\clearpage
+\section{Sample layout for tables}
+Suggestions.
+\begin{itemize}
+    \item The caption should be at the top of the table.
+    \item The text should not be too small.
+    \item 
+\end{itemize}
 
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a
-discussion of the policy on dual submissions.
+% single column
+\input{tables/table1}
+\input{tables/table2}
+\input{tables/table3}
+\input{tables/table4}
+\input{tables/table5}
+\input{tables/table6}
+\input{tables/table_network2}
 
-\subsection{Paper length}
-Papers, excluding the references section, must be no longer than eight pages in length.
-The references section will not be included in the page count, and there is no limit on the length of the references section.
-For example, a paper of eight pages with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for \confName\ \confYear.}
+\input{tables/table_figure1}
 
-Overlength papers will simply not be reviewed.
-This includes papers where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.
-Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for supervised revisions of manuscripts.
-The reviewing process cannot determine the suitability of the paper for presentation in eight pages if it is reviewed in eleven.
+% two column
+\input{tables/table8}
+\input{tables/table9}
+\input{tables/table7}
+\input{tables/table_figure2}
 
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the version submitted for review.
-The ruler is provided in order that reviewers may comment on particular lines in the paper without circumlocution.
-If you are preparing a document using a non-\LaTeX\ document preparation system, please arrange for an equivalent ruler to appear on the final output pages.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera-ready copy should not contain a ruler.
-(\LaTeX\ users may use options of cvpr.sty to switch between different versions.)
+\input{tables/table_network1}
 
-Reviewers:
-note that the ruler measurements do not align well with lines in the paper --- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-Just use fractional references (\eg, this line is $087.5$), although in most cases one would expect that the approximate location will be adequate.
-
-\subsection{Paper ID}
-Make sure that the Paper ID from the submission system is visible in the version submitted for review (replacing the ``*****'' you see in this document).
-If you are using the \LaTeX\ template, \textbf{make sure to update paper ID in the appropriate place in the tex file}.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations as in these examples:
-\begin{equation}
-  E = m\cdot c^2
-  \label{eq:important}
-\end{equation}
-and
-\begin{equation}
-  v = a\cdot t.
-  \label{eq:also-important}
-\end{equation}
-It is important for readers to be able to refer to any particular equation.
-Just because you did not refer to it in the text does not mean some future reader might not need to refer to it.
-It is cumbersome to have to use circumlocutions like ``the equation second from the top of page 3 column 1''.
-(Note that the ruler will not be present in the final copy, so is not an alternative to equation numbers).
-All authors will benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind review.
-Blind review does not mean that one must remove citations to one's own work---in fact it is often impossible to review a paper unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our'' when citing previous work.
-That is all.
-(But see below for tech reports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that you are Lucy Smith;
-it says that you are building on her work.
-If you are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith and Jones show in [7]'' and at the end of the paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our previous paper [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the  paper of Smith \etal [1], and show it to be inferior to all previously known methods.
-   Why the previous paper was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a fundamental contribution to human knowledge''. Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time, which covers similar or overlapping material, you may need to refer to that submission in order to explain the differences, just as you would if you had previously published related work.
-In such cases, include the anonymized parallel submission~\cite{Authors14} as supplemental material and cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324, Supplied as supplemental material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be found elsewhere, and refer them to a technical report.
-For conference submissions, the paper must stand on its own, and not {\em require} the reviewer to go to a tech report for further details.
-Thus, you may say in the body of the paper ``further details may be found in~\cite{Authors14b}''.
-Then submit the tech report as supplemental material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool that is widely known to be restricted to a single institution.
-For example, let's say it's 1969, you have solved a key problem on the Apollo lander, and you believe that the CVPR70 audience would like to hear about your
-solution.
-The work is a development of your celebrated 1968 paper entitled ``Zero-g frobnication: How being the only people in the world with access to the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.
-Do not write ``We show how to improve our previous work [Anonymous, 1968].
-This time we tested the algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors.
-Instead write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.
-   This system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] did not  handle case B properly.
-   Ours handles it by including a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo lunar lander, and went all the way to the moon, don't you know.
-   It displayed the following behaviours, which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention, reads better than the first version, and does not explicitly name you as the authors.
-A reviewer might think it likely that the new paper was written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double-blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-  \centering
-  \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-
-   \caption{Example of caption.
-   It is set in Roman so that mathematics (always set in Roman: $B \sin A = A \sin B$) may be included without an ugly clash.}
-   \label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a sentence-ending space.
-So \eg is correct, {\em e.g.} is not.
-The provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word).
-If you use the \verb'\etal' macro provided, then you need not worry about double periods when used at the end of a sentence as in Alpher \etal.
-However, use it only when there are three or more authors.
-Thus, the following is correct:
-   ``Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...'' because reference~\cite{Alpher03} has just two authors.
-
-% Update the cvpr.cls to do the following automatically.
-% For this citation style, keep multiple citations in numerical (not
-% chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-% \cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}{0.68\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{An example of a subfigure.}
-    \label{fig:short-a}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{0.28\linewidth}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-    \caption{Another example of a subfigure.}
-    \label{fig:short-b}
-  \end{subfigure}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-\label{sec:formatting}
-
-All text must be in a two-column format.
-The total allowable size of the text area is $6\frac78$ inches (17.46 cm) wide by $8\frac78$ inches (22.54 cm) high.
-Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch (0.8 cm) space between them.
-The main title (on the first page) should begin 1 inch (2.54 cm) from the top edge of the page.
-The second and following pages should begin 1 inch (2.54 cm) from the top edge.
-On all pages, the bottom margin should be $1\frac{1}{8}$ inches (2.86 cm) from the bottom edge of the page for $8.5 \times 11$-inch paper;
-for A4 paper, approximately $1\frac{5}{8}$ inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area $6\frac{7}{8}$ inches (17.46 cm) wide by $8\frac{7}{8}$ inches (22.54 cm)
-high.
-%
-Page numbers should be in the footer, centered and $\frac{3}{4}$ inches from the bottom of the page.
-The review version should have page numbers, yet the final version submitted as camera ready should not show any page numbers.
-The \LaTeX\ template takes care of this when used properly.
-
-%-------------------------------------------------------------------------
-\subsection{Type style and fonts}
-
-Wherever Times is specified, Times Roman may also be used.
-If neither is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE.
-Center the title $1\frac{3}{8}$ inches (3.49 cm) from the top edge of the first page.
-The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and adverbs;
-do not capitalize articles, coordinate conjunctions, or prepositions (unless the title begins with such a word).
-Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type.
-This information is to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT.
-Type main text in 10-point Times, single-spaced.
-Do NOT use double-spacing.
-All paragraphs should be indented 1 pica (approx.~$\frac{1}{6}$ inch or 0.422 cm).
-Make sure your text is fully justified---that is, flush left and flush right.
-Please do not place any additional blank lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in \cref{fig:onecol,fig:short}.
-Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-, second-, and third-order headings.
-
-FIRST-ORDER HEADINGS.
-(For example, {\large \bf 1. Introduction}) should be Times 12-point boldface, initially capitalized, flush left, with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS.
-(For example, { \bf 1.1. Database elements}) should be Times 11-point boldface, initially capitalized, flush left, with one blank line before, and one after.
-If you require a third-order heading (we discourage it), use 10-point Times, boldface, initially capitalized, flush left, preceded by one blank line, followed by a period and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote{This is what a footnote looks like.
-It often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral observations in the text (within parentheses, if you prefer, as in this sentence).
-If you wish to use a footnote, place it at the bottom of the column on the page on which it is referenced.
-Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{Cross-references}
-
-For the benefit of author(s) and readers, please use the
-{\small\begin{verbatim}
-  \cref{...}
-\end{verbatim}}  command for cross-referencing to figures, tables, equations, or sections.
-This will automatically insert the appropriate label alongside the cross-reference as in this example:
-\begin{quotation}
-  To see how our method outperforms previous work, please see \cref{fig:onecol} and \cref{tab:example}.
-  It is also possible to refer to multiple targets as once, \eg~to \cref{fig:onecol,fig:short-a}.
-  You may also return to \cref{sec:formatting} or look at \cref{eq:also-important}.
-\end{quotation}
-If you do not wish to abbreviate the label, for example at the beginning of the sentence, you can use the
-{\small\begin{verbatim}
-  \Cref{...}
-\end{verbatim}}
-command. Here is an example:
-\begin{quotation}
-  \Cref{fig:onecol} is also quite important.
-\end{quotation}
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times, single-spaced, at the end of your paper.
-When referenced in the text, enclose the citation number in square brackets, for
-example~\cite{Authors14}.
-Where appropriate, include page numbers and the name(s) of editors of referenced books.
-When you cite multiple papers at once, please make sure that you cite them in numerical order like this \cite{Alpher02,Alpher03,Alpher05,Authors14b,Authors14}.
-If you use the template as advised, this will be taken care of automatically.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lc@{}}
-    \toprule
-    Method & Frobnability \\
-    \midrule
-    Theirs & Frumpy \\
-    Yours & Frobbly \\
-    Ours & Makes one's heart Frob\\
-    \bottomrule
-  \end{tabular}
-  \caption{Results.   Ours is better.}
-  \label{tab:example}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.
-In \LaTeX, avoid using the \texttt{center} environment for this purpose, as this adds potentially unwanted whitespace.
-Instead use
-{\small\begin{verbatim}
-  \centering
-\end{verbatim}}
-at the beginning of your figure.
-Please ensure that any point you wish to make is resolvable in a printed copy of the paper.
-Resize fonts in figures to match the font in the body text, and choose line widths that render effectively in print.
-Readers (and reviewers), even of an electronic copy, may choose to print your paper in order to read it.
-You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the figure width as a multiple of the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.pdf}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the \confName\ \confYear\ web page for a discussion of the use of color in your document.
-
-If you use color in your plots, please keep in mind that a significant subset of reviewers and readers may have a color vision deficiency; red-green blindness is the most frequent kind.
-Hence avoid relying only on color as the discriminative feature in plots (such as red \vs green lines), but add a second discriminative feature to ease disambiguation.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit your finished paper.
-We MUST have this form before your paper can be published in the proceedings.
-
-Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
-\url{https://www.computer.org/about/contact}.
-
+\clearpage
 %%%%%%%%% REFERENCES

### 2021-11-19 tables/table3.tex
Add tables

% require package makecell 
\begin{table}[thb]\centering
    \caption{A table with line break in the header. Line break is useful if the item name is too long.}
    \label{tab:table3}
    \resizebox{0.48\textwidth}{!}{
    \large
    \begin{tabular}{*{10}{c}}
        \toprule
         %&  &  \multicolumn{3}{c}{\makecell{Static Scenes \\ w/ Ground Truth}} & \multicolumn{3}{c}{\makecell{Dynamic Scenes \\ w/o Ground Truth}} \\
        &  &  \multicolumn{3}{c}{$6-9$ frames} & \multicolumn{3}{c}{$5-7$ frames} \\
        Data & Size &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} \\
        \midrule
        A & $1280\times 720$ & 1 & 2 & 3 & 4 & 5 & 4 \\
        Ours & $4096\times 2168$ & 2 & 3 & 4 & 6 & 5 & 4 \\
        \bottomrule
    \end{tabular}
    }
\end{table}

### 2021-11-19 tables/table4.tex
Add tables

--- 2021-11-19 tables/table3.tex
@@
 \begin{table}[thb]\centering
-    \caption{A table with line break in the header. Line break is useful if the item name is too long.}
-    \label{tab:table3}
+    \caption{A table with multi-column headers and vertical lines for grouping.}
+    \label{tab:table4}
     \resizebox{0.48\textwidth}{!}{
     \large
-    \begin{tabular}{*{10}{c}}
+    \begin{tabular}{c|c|ccc|ccc}
         \toprule
          %&  &  \multicolumn{3}{c}{\makecell{Static Scenes \\ w/ Ground Truth}} & \multicolumn{3}{c}{\makecell{Dynamic Scenes \\ w/o Ground Truth}} \\
-        &  &  \multicolumn{3}{c}{$6-9$ frames} & \multicolumn{3}{c}{$5-7$ frames} \\
+        &  &  \multicolumn{3}{c|}{$6-9$ frames} & \multicolumn{3}{c}{$5-7$ frames} \\
         Data & Size &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} \\

### 2021-11-19 tables/table5.tex
Add tables

% require package makecell 
\begin{table}[thb]\centering
    \caption{A table with multi-column headers and bold font highlights.}
    \label{tab:table5}
    \resizebox{0.48\textwidth}{!}{
    \large
    \begin{tabular}{c|c|ccc|ccc}
        \toprule
         %&  &  \multicolumn{3}{c}{\makecell{Static Scenes \\ w/ Ground Truth}} & \multicolumn{3}{c}{\makecell{Dynamic Scenes \\ w/o Ground Truth}} \\
        &  &  \multicolumn{3}{c|}{$6-9$ frames} & \multicolumn{3}{c}{$5-7$ frames} \\
        Data & Size &  \makecell{2-Exp \\ Break} &  \makecell{2-Exp \\ Break} &  \makecell{2-Exp \\ Break} &  \makecell{2-Exp \\ Break} &  \makecell{2-Exp \\ Break} &  \makecell{2-Exp \\ Break} \\
        \midrule
        A & $1280\times 720$ & 1 & 2 & 3 & 4 & \textbf{5} & \textbf{7} \\
        Ours & $4096\times 2168$ & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{6} & \textbf{5} & 4 \\
        \bottomrule
    \end{tabular}
    }
\end{table}

### 2021-11-19 tables/table6.tex
Add tables

% \usepackage{colortbl}  
% \usepackage{xcolor}

\begin{table}[thb]\centering
    \caption{a table with parallel lines for grouping and color highlight.} %
    \label{tab:ablation_study}
    \resizebox{0.48\textwidth}{!}{
    \Large
    \begin{tabular}{*{2}{l}||*{2}{c}||*{2}{c}||*{2}{c}}
        \toprule
        \multicolumn{1}{c}{} & \multicolumn{1}{c||}{} & \multicolumn{2}{c||}{Synthetic Dataset} & \multicolumn{2}{c||}{Static Data} & \multicolumn{2}{c}{Dynamicgt Data} \\
        ID & Method  & PSNRT & VDP & PSNRT & VDP & PSNRT & VDP \\
        \midrule
        0 & ANet  & 39.25 & 70.81 & 40.62 & 74.51 & 44.43 & 77.74 \\ %
        1 & BNet  & 39.69 & 70.95 & 37.61 & 75.30 & 43.70 & 78.97 \\
        \rowcolor{gray!20}
        2 & ANet + BNet  & \textbf{40.34} & \textbf{71.79} & \textbf{41.18} & \textbf{76.15} & \textbf{45.46} & \textbf{79.09} \\
        \midrule
        3 & ANet + BNet w/o C & 39.72 & 71.38 & 40.52 & 74.79 & 45.09 & 78.24 \\ %
        4 & ANet + BNet w/o D & 40.03 & 71.66 & 40.80 & 76.12 & 45.17 & 78.99 \\ %
        \bottomrule
    \end{tabular}
    }
\end{table}

### 2021-11-19 tables/table9.tex
Add tables

\begin{table*} \centering
    \caption{A two-column table with color header.}
    \label{tab:table9}
    \begin{minipage}{0.93\textwidth}
    \resizebox{\textwidth}{!}{
    \Huge
        \begin{tabular}{c|*{4}{c}|*{4}{c}|*{4}{c}|*{4}{c}|*{4}{c}}
        \toprule
        & \multicolumn{4}{c}{Glass} 
                               & \multicolumn{4}{c}{Glass with Water} 
                               & \multicolumn{4}{c}{Lens} 
                               & \multicolumn{4}{c}{Complex Shape}  
                               & \multicolumn{4}{c}{Average}  \\
                               & \cellcolor{red!25} F-EPE & \cellcolor{red!25}A-MSE & \cellcolor{red!25}I-MSE & \cellcolor{blue!25} M-IoU 
                               & \cellcolor{red!25} F-EPE & \cellcolor{red!25}A-MSE & \cellcolor{red!25}I-MSE & \cellcolor{blue!25} M-IoU 
                               & \cellcolor{red!25} F-EPE & \cellcolor{red!25}A-MSE & \cellcolor{red!25}I-MSE & \cellcolor{blue!25} M-IoU 
                               & \cellcolor{red!25} F-EPE & \cellcolor{red!25}A-MSE & \cellcolor{red!25}I-MSE & \cellcolor{blue!25} M-IoU 
                               & \cellcolor{red!25} F-EPE & \cellcolor{red!25}A-MSE & \cellcolor{red!25}I-MSE & \cellcolor{blue!25} M-IoU \\
        \midrule
        Method A    & 3.6 / 30.3 & 1.33 & 0.48 & 0.12 & 6.4 / 53.2 & 1.54 & 0.68 & 0.12 & 10.3 / 39.2 & 1.94 & 1.57 & 0.24 & 6.8 / 56.8 & 2.50 & 0.85 & 0.11 & 6.8 / 44.9 & 1.83 & 0.90 & 0.15 \\
        Method B     & 2.1 / 15.8 & 0.22 & 0.14 & 0.97 & 3.1 / 23.5 & 0.31 & 0.23 & 0.97 & 2.0 / 6.7   & 0.17 & 0.28 & 0.99 & 4.5 / 34.4 & 0.38 & 0.33 & 0.92 & 2.9 / 20.1 & 0.27 & 0.24 & 0.96 \\
        \midrule
        Method C       & 1.9 / 14.7 & 0.21 & 0.14 & 0.97 & 2.9 / 21.8 & 0.30 & 0.22 & 0.97 & 1.9 / 6.6   & 0.15 & 0.29 & 0.99 & 4.1 / 31.5 & 0.37 & 0.32 & 0.92 & 2.7 / 18.6 & 0.26 & 0.24 & 0.96 \\
        \bottomrule
    \end{tabular}
    }
    \end{minipage}
    \hspace{-0.6em}
    \begin{minipage}{0.06\textwidth}
        \resizebox{\textwidth}{!}{
        \begin{tabular}{cc}
            \midrule
            MSE ($\cdot10^{-2}$) \\
            \cellcolor{red!25} $\downarrow$ better \\ 
            \cellcolor{blue!25} $\uparrow$ better\\
            \midrule
        \end{tabular}
        }
    \end{minipage}
\end{table*}

### 2021-11-19 paper_writing_tips.tex
Add figures

@@
     \item Contributions
-\end{itemize}
-
-\clearpage
-\section{Sample layout for figures}
-\begin{itemize}
-    \item The caption should be at the bottom of the figure. 
+    \item Use Figure x at the beginning of the sentence, and Fig.~x else where.
+    \item Also use Table~x when referring table.
 \end{itemize}
@@
     \item The text should not be too small.
-    \item 
+    \item It is better to put the table at top of the paper.
 \end{itemize}
@@
 % single column
-\input{tables/table1}
-\input{tables/table2}
-\input{tables/table3}
-\input{tables/table4}
-\input{tables/table5}
-\input{tables/table6}
-\input{tables/table_network2}
+\input{tables/table1} % simple table
+\input{tables/table2} % multi-column table
+\input{tables/table3} % multi-column with makecell
+\input{tables/table4} % multi-column with vertical lines
+\input{tables/table5} % multi-column with bold font
+\input{tables/table6} % multi-column with parallel lines
+\input{tables/table_network2} % single-column network arch
 
-\input{tables/table_figure1}
+\input{tables/table_figure1} % table with images
 
 % two column
-\input{tables/table8}
-\input{tables/table9}
-\input{tables/table7}
-\input{tables/table_figure2}
+\input{tables/table8} % two-column table
+\input{tables/table9} % two-column table with color header
+\input{tables/table7} % two-column table with two sub-tables
+\input{tables/table_figure2} % two-column tables with images in the header
 
-\input{tables/table_network1}
+\input{tables/table_network1} % two column network arch table
+
+\clearpage
+\section{Sample layout for figures}
+\begin{itemize}
+    \item The caption should be at the bottom of the figure. 
+\end{itemize}
+
+% Single-column
+\input{figures/figure1} % single image
+\input{figures/figure2} % two images
+\input{figures/figure3} % four images
+\input{figures/figure4} % four images with text header
+\input{figures/figure5} % four images with vertical text
+\input{figures/figure6} % two sub figures
+
+% Two column
+\input{figures/figure7} % single image
+\input{figures/figure8} % multiple images
+\input{figures/figure9} % 
+\input{figures/figure10} % 
+\input{figures/figure11} %
 

### 2021-11-19 paper_writing_tips.tex
Add figures

@@
 \input{tables/table_figure2} % two-column tables with images in the header
+\input{tables/table10} % two tables side-by-side
+\input{tables/table11} % table with caption at the left
 
@@
 \input{figures/figure8} % multiple images
-\input{figures/figure9} % 
-\input{figures/figure10} % 
-\input{figures/figure11} %
+\input{figures/figure9} % multiple images with two zoom in patches (horizontal)
+\input{figures/figure11} % multiple images with two zoom in patches (vertical) 
+\input{figures/figure13} % two figure placed side-by-side
+\input{figures/figure12} % figure with caption at the left
+
+\input{figures/figure10} % multiple images organized with multi-level
 

### 2021-11-19 tables/table10.tex
Add figures

--- 2021-11-19 tables/table3.tex
@@
-% require package makecell 
-\begin{table}[thb]\centering
-    \caption{A table with line break in the header. Line break is useful if the item name is too long.}
-    \label{tab:table3}
-    \resizebox{0.48\textwidth}{!}{
+\begin{table*}[t] \centering
+\begin{minipage}[t]{0.48\linewidth}
+    \caption{Two tables placed side by side. Table A (left).} \label{tab:table10A}
+    \resizebox{\textwidth}{!}{
+    \large
+    \begin{tabular}{*{10}{c}}
+        \toprule
+        &  &  \multicolumn{2}{c}{$6-9$ frames} & \multicolumn{2}{c}{$5-7$ frames} & \multicolumn{2}{c}{$50-200$ frames} \\
+       Data & Size &  2-Exp & 3-Exp &  2-Exp & 3-Exp &  2-Exp & 3-Exp \\
+        \midrule
+        A & $1280\times 720$ & 1 & 2 & 3 & 4 & 5 & 4 \\
+        Ours & $4096\times 2168$ & 2 & 3 & 4 & 6 & 5 & 4 \\
+        \bottomrule
+    \end{tabular}
+    }
+\end{minipage}\hfill
+    \begin{minipage}[t]{0.48\linewidth}
+    \caption{Two tables placed side by side. Table B (right).} \label{tab:table10B}
+    \resizebox{\textwidth}{!}{
     \large
@@
     }
-\end{table}
+\end{minipage}
+\end{table*}

### 2021-11-19 tables/table11.tex
Add figures

--- 2021-11-19 tables/table10.tex
@@
-\begin{table*}[t] \centering
-\begin{minipage}[t]{0.48\linewidth}
-    \caption{Two tables placed side by side. Table A (left).} \label{tab:table10A}
+\begin{table*}[t]
+\begin{minipage}[c]{0.48\textwidth} \centering
+    \caption{A table with caption at the right. This is useful for single-column paper (\eg, ECCV), where space are limited.} \label{tab:table11}
+\end{minipage}\hfill
+\begin{minipage}[c]{0.48\textwidth}\centering
     \resizebox{\textwidth}{!}{
@@
     }
-\end{minipage}\hfill
-    \begin{minipage}[t]{0.48\linewidth}
-    \caption{Two tables placed side by side. Table B (right).} \label{tab:table10B}
-    \resizebox{\textwidth}{!}{
-    \large
-    \begin{tabular}{*{10}{c}}
-        \toprule
-         %&  &  \multicolumn{3}{c}{\makecell{Static Scenes \\ w/ Ground Truth}} & \multicolumn{3}{c}{\makecell{Dynamic Scenes \\ w/o Ground Truth}} \\
-        &  &  \multicolumn{3}{c}{$6-9$ frames} & \multicolumn{3}{c}{$5-7$ frames} \\
-        Data & Size &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} &  \makecell{2-Exp \\ Scenes} \\
-        \midrule
-        A & $1280\times 720$ & 1 & 2 & 3 & 4 & 5 & 4 \\
-        Ours & $4096\times 2168$ & 2 & 3 & 4 & 6 & 5 & 4 \\
-        \bottomrule
-    \end{tabular}
-    }
 \end{minipage}

### 2021-11-19 figures/figure_plot1.tex
Upate figure

\begin{figure}[t] \centering
\tdplotsetmaincoords{70}{105}
%
\pgfmathsetmacro{\rvec}{1}
\pgfmathsetmacro{\thetavec}{40}
\pgfmathsetmacro{\phivec}{45}
%
\begin{tikzpicture}[scale=1.7,tdplot_main_coords]
    \coordinate (O) at (0,0,0); % Coordinate
    \draw[->] (0,0,0) -- (1,0,0) node[below=0.5ex,left=-0.4ex]{$z$};
    \draw[->] (0,0,0) -- (0,1,0) node[right=-0.4ex]{$x$};
    \draw[->] (0,0,0) -- (0,0,1) node[above=-0.4ex]{$y$};
    \draw[dashed,color=gray] (0,0,0) -- (0,0,-1);
    \draw[dashed,color=gray] (0,0,0) -- (0,-1,0);
    \tdplotdrawarc[dashed,color=gray]{(O)}{1}{-90}{90}{}{}
    \tdplotsetthetaplanecoords{0}
    \tdplotdrawarc[semithick,dashed,color=gray,tdplot_rotated_coords]{(0,0,0)}{1}{0}{180}{}{}
    \tdplotsetthetaplanecoords{90}
    \tdplotdrawarc[semithick,dashed,color=gray,tdplot_rotated_coords]{(0,0,0)}{1}{0}{360}{}{}

    \tdplotsetcoord{P}{\rvec}{\thetavec}{\phivec} % Draw vector P
    \draw[line width=1pt,-stealth,color=black] (O) -- (P) node[above right] {$P$};

    % Draw arc for angle
    \tdplotsetcoord{Px}{\rvec}{90}{\phivec} % Azimuth
    \draw[dashed, color=black] (O) -- (Px);
    \tdplotdrawarc[thick,color=red]{(O)}{0.4}{\phivec}{90}{color=red,below=0.4ex,right=-0.4ex}{$\phi$}

    \tdplotsetthetaplanecoords{\phivec} % Elevation
    \tdplotdrawarc[tdplot_rotated_coords,thick,color=blue,opacity=0.8]{(0,0,0)}{0.4}{\thetavec}{90}{above=0.4ex,right=-0.5ex}{$\theta$}
    \tdplotdrawarc[semithick,dashed,color=gray,tdplot_rotated_coords]{(0,0,0)}{1}{0}{180}{}{}
\end{tikzpicture}

\tdplotsetmaincoords{70}{100}
%
\pgfmathsetmacro{\rvec}{1}
\pgfmathsetmacro{\thetavec}{52}
\pgfmathsetmacro{\phivec}{45}
%
\pgfmathsetmacro{\dev}{18}
\pgfmathsetmacro{\tha}{\thetavec-\dev}
\pgfmathsetmacro{\thb}{\thetavec+\dev}
\pgfmathsetmacro{\phia}{\phivec-\dev}
\pgfmathsetmacro{\phib}{\phivec+\dev}

\begin{tikzpicture}[scale=1.7,tdplot_main_coords]
    \coordinate (O) at (0,0,0); % Coordinate
    %\draw[semithick,->] (0,0,0) -- (1,0,0) node[left]{$y$};
    %\draw[semithick,->] (0,0,0) -- (0,1,0) node[anchor=north]{$x$};
    %\draw[semithick,->] (0,0,0) -- (0,0,1) node[anchor=south]{$z$};
    \draw[->] (0,0,0) -- (1,0,0) node[below=0.5ex,left=-0.4ex]{$z$};
    \draw[->] (0,0,0) -- (0,1,0) node[right=-0.4ex]{$x$};
    \draw[->] (0,0,0) -- (0,0,1) node[above=-0.4ex]{$y$};
    \draw[dashed,color=gray] (0,0,0) -- (0,0,-1);
    \draw[dashed,color=gray] (0,0,0) -- (0,-1,0);
    \tdplotdrawarc[semithick,dashed,color=gray]{(O)}{1}{-90}{90}{}{}
    \tdplotsetthetaplanecoords{90}
    \tdplotdrawarc[semithick,dashed,color=gray,tdplot_rotated_coords]{(0,0,0)}{1}{0}{360}{}{}

    \tdplotsetcoord{P}{\rvec}{\thetavec}{\phivec} % Draw vector P
    \draw[thick,-stealth,color=black] (O) -- (P) node[below=0.2ex,right=-1.0ex] {$P$};

    \tdplotsetcoord{Pa}{\rvec}{\tha}{\phia}
    \tdplotsetcoord{Pb}{\rvec}{\tha}{\phib}
    \tdplotsetcoord{Pc}{\rvec}{\thb}{\phia}
    \tdplotsetcoord{Pd}{\rvec}{\thb}{\phib}
    \tdplotsetcoord{Pf}{\rvec}{\tha}{\phivec}

    \draw[color=black] (O) -- (Pa) node[above=0.2ex,left=-0.7ex] {\color{black!90}\scriptsize $A$};
    \draw[color=black] (O) -- (Pb) node[above,right=-0.3ex] {\color{black!90}\scriptsize $B$};
    \draw[color=black] (O) -- (Pc) node[below=1.2ex,left=-0.9ex] {\color{black!90}\scriptsize $C$};
    \draw[color=black] (O) -- (Pd) node[below=0.2ex,right=-0.3ex] {\color{black!90}\scriptsize $D$};
    \draw[color=blue,dashed] (O) -- (Pf) node[above left] {};

    \draw[semithick,color=red] (Pa) to  (Pb) node[below left] {};
    \draw[semithick,color=red] (Pd) to  (Pc) node[below left] {};

    \tdplotsetthetaplanecoords{\phivec}
    \tdplotdrawarc[thick,color=blue,opacity=0.8,tdplot_rotated_coords]{(0,0,0)}{0.7}{\tha}{\thetavec}{above=0.7ex,right=-0.7ex}{\small $\delta$}
    \tdplotsetthetaplanecoords{\phia}
    \tdplotdrawarc[semithick,color=red,tdplot_rotated_coords]{(0,0,0)}{\rvec}{\tha}{\thb}{anchor=south west}{}
    \tdplotdrawarc[dashed,tdplot_rotated_coords]{(0,0,0)}{\rvec}{0}{\tha}{anchor=south west}{}
    \tdplotdrawarc[dashed,tdplot_rotated_coords]{(0,0,0)}{\rvec}{\thb}{180}{anchor=south west}{}
    \tdplotsetthetaplanecoords{\phib}
    \tdplotdrawarc[semithick,color=red,tdplot_rotated_coords]{(0,0,0)}{\rvec}{\tha}{\thb}{anchor=south west}{}
    \tdplotdrawarc[dashed,tdplot_rotated_coords]{(0,0,0)}{\rvec}{0}{\tha}{anchor=south west}{}
    \tdplotdrawarc[dashed,tdplot_rotated_coords]{(0,0,0)}{\rvec}{\thb}{180}{anchor=south west}{}
    % Draw arc for angle
    %\tdplotsetcoord{Px}{\rvec}{90}{\phivec} % Azimuth
    %\draw[dashed, color=black] (O) -- (Px);
    %\tdplotdrawarc[thick,color=red]{(O)}{0.4}{\phivec}{90}{color=red,below=0.3ex,right}{$\phi$}

    %\tdplotsetthetaplanecoords{\phivec} % Elevation
    %\tdplotdrawarc[tdplot_rotated_coords,thick,color=blue,opacity=0.8]{(0,0,0)}{0.4}{\thetavec}{90}{above=0.1ex,right=-0.5ex}{$\theta$}
    %\tdplotdrawarc[semithick,dashed,color=gray,tdplot_rotated_coords]{(0,0,0)}{1}{0}{90}{}{}
\end{tikzpicture}

    \vspace{-0.6em} \makebox[0.22\textwidth]{\small (a)} \hfill \makebox[0.23\textwidth]{\small (b)}
    \caption{(a) Light directions $A, B, C$, and $D$ have the maximum deviation angles with the light direction $P$ after discretization. (b) Upper-bound of normal estimation error for PS-FCN~\cite{chen2018ps} under different light direction space discretization levels ($\infty$ indicates no discretization).} \label{fig:discretization}
\end{figure}

### 2021-11-19 paper_writing_tips.tex
v1

@@
 %\usepackage[review]{cvpr}      % To produce the REVIEW version
-\usepackage{cvpr}              % To produce the CAMERA-READY version
-%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
+%\usepackage{cvpr}              % To produce the CAMERA-READY version
+\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version
 
@@
 %%%%%%%%% TITLE - PLEASE UPDATE
-\title{LaTex Paper Writing Tips for Beginners}
+\title{Tips for Writing a Research Paper using \LaTeX}
 
 \author{Guanying Chen \\
-{\tt\small guanying2018@gmail.com}
+{\tt\small \url{https://guanyingc.github.io}}
 % For a paper whose authors are all at the same institution,
@@
 \label{sec:intro}
+\LaTeX\ is a very powerful tool for documentation preparation, and is often used by researchers to prepare a manuscript for reviewing and publication. 
+However, some new graduate students might not have experience in using \LaTeX and thus have a difficult time in prepare their first paper.
 
-\section{Common Mistakes}
+In this article, we will first provide some tips for paper writing.  
+using \LaTeX. 
+Then, we will showcase several working examples for the table and figure, which have been used in my previous publications.
+The readers are encouraged to adapt those tables and figures to their purposes to save time.
+
+\section{Tips for the Writing}
+In this section, we provide some tips for paper writing. 
 \begin{itemize}
-    \item There should be a space before the open parentheses: [\wrong{hello(word)}, \correct{hello (word)}].
-    \item citation
-    \item There should be no space before the punctuation (\eg, ,. ').
-    \item \ie, \eg
-    \item Do not add citations in the abstract
-    \item Every equation should end with a punctuation.
-    \item The first character should be capitalized
-    \item keep the same tense
-    \item
-    \item
-    \item
-    \item
-    \item
-    \item
-    \item
-\end{itemize}
-
-\section{Suggestions}
-\begin{itemize}
-    \item use newcommand for abbr
-    \item Fig/Tab.
-    \item use newcommand in equation
-    \item Principal: be compact and clear.
-    \item Contributions
-    \item Use Figure x at the beginning of the sentence, and Fig.~x else where.
-    \item Also use Table~x when referring table.
+    \item There should be a space before the open parentheses:\\
+        \wrong{Convolutional neural network(CNN) has been successfully applied on various vision problems.}\\
+        \correct{Convolutional neural network (CNN) has been successfully applied on various vision problems.}
+    \item There should be no space before the period and comma punctuation marks:\\
+        \wrong{Convolutional neural network (CNN) has been successfully applied on various vision problems .}\\
+        \correct{Convolutional neural network (CNN) has been successfully applied on various vision problems.}
+    \item There should be a punctuation at the end of the equation:
+        \begin{align}
+            \label{eq:eq1}
+            & \textcolor{red}{E = mc^2 \quad \times} \\
+            & \textcolor{blue}{E = mc^2. \quad \checkmark}
+        \end{align}
+    \item All equations should be numbered:
+        \begin{align}
+            \label{eq:eq2} \nonumber
+            & \textcolor{red}{E = mc^2. \quad \times}\\ 
+            & \textcolor{blue}{E = mc^2. \quad \checkmark}
+        \end{align}
+    \item The first character in a sentence should be capitalized:\\
+        \wrong{how are you?}\\
+        \correct{How are you?}
+    \item Double quotation marks should be correctly typed:\\
+        \wrong{Are you "okay"?}\\
+        \correct{Are you ``okay''?}
+    \item There should be a space before the citation:\\
+        \wrong{A proposes a method B for this problem[1].}\\
+        \correct{A proposes a method B for this problem~[1].}
+    \item Do not include citations in the abstract.
+    \item Use \textbackslash ie command for \ie and use \textbackslash eg for \eg.
+    \item Define a macro for a word or phrase if it appears frequently (\eg, the method name and the dataset name).
+The command can be\\``\textbackslash newcommand\{\textbackslash NetName\}\{A Great Deep Net\}''.
+    \item When referring to a table, also use ``Table~\ref{tab:table1}'' in a sentence.
+    \item The table caption should be at the top of the table.
+    \item When referring to a figure, use ``Figure~\ref{fig:figure1}'' at the beginning, and ``Fig.~\ref{fig:figure1}'' at the middle or the end of a sentence.
+    \item The figure caption should be at the bottom of the table.
+    \item It is better to put the tables and figures at the top of a page.
 \end{itemize}
@@
 \clearpage
-\section{Sample layout for tables}
-Suggestions.
-\begin{itemize}
-    \item The caption should be at the top of the table.
-    \item The text should not be too small.
-    \item It is better to put the table at top of the paper.
-\end{itemize}
+\section{Examples for the Tables}
 
@@
 \input{tables/table5} % multi-column with bold font
+\newpage
 \input{tables/table6} % multi-column with parallel lines
@@
 \input{tables/table8} % two-column table
+\input{tables/table12} % two-column table with remarks
 \input{tables/table9} % two-column table with color header
@@
 \clearpage
-\section{Sample layout for figures}
-\begin{itemize}
-    \item The caption should be at the bottom of the figure. 
-\end{itemize}
+\clearpage
+
+\section{Examples for Figures}
 
@@
 \input{figures/figure6} % two sub figures
+\input{figures/figure15} % figure numeric results and color bar
 
@@
 \input{figures/figure12} % figure with caption at the left
+\input{figures/figure14} % figure numeric results and color bar
 
@@
 
-\clearpage
+%\clearpage
 %%%%%%%%% REFERENCES
-{\small
-\bibliographystyle{ieee_fullname}
-\bibliography{egbib}
-}
+%{\small
+%\bibliographystyle{ieee_fullname}
+%\bibliography{egbib}
+%}
 

### 2021-11-19 paper_writing_tips.tex
Fix minors

@@
 In this article, we will first provide some tips for paper writing.  
-using \LaTeX. 
-Then, we will showcase several working examples for the table and figure, which have been used in my previous publications.
-The readers are encouraged to adapt those tables and figures to their purposes to save time.
+Then, we will showcase several working examples for the tables and figures, which have been used in our previous publications.
+The readers are encouraged to adapt those tables and figures to their purposes to save time when preparing their first papers.
 
@@
 \input{tables/table10} % two tables side-by-side
+
+\clearpage
 \input{tables/table11} % table with caption at the left
@@
 \input{figures/figure14} % figure numeric results and color bar
-
 \input{figures/figure10} % multiple images organized with multi-level

### 2021-11-20 paper_writing_tips.tex
Fix minors
Update toc and tables

@@
 \captionsetup[figure]{belowskip=0pt}
-\captionsetup{font=small}
+\captionsetup{font=normal}
 
@@
 }
+\onecolumn
 \maketitle
@@
 %%%%%%%%% BODY TEXT
-\vspace{6em}
+%\newpage
+\vspace{7em}
+
 \section{Introduction}
@@
 
+\twocolumn
+
 \section{Tips for the Writing}
-In this section, we provide some tips for paper writing. 
+In this section, we point out some common mistakes in paper writing and give some suggestions for editing \LaTeX\ files.
+
+\subsection{Some Common Mistakes}
 \begin{itemize}
@@
         \correct{A proposes a method B for this problem~[1].}
+\end{itemize}
+
+\subsection{Some Suggestions}
+\begin{itemize}
     \item Do not include citations in the abstract.
-    \item Use \textbackslash ie command for \ie and use \textbackslash eg for \eg.
     \item Define a macro for a word or phrase if it appears frequently (\eg, the method name and the dataset name).
 The command can be\\``\textbackslash newcommand\{\textbackslash NetName\}\{A Great Deep Net\}''.
-    \item When referring to a table, also use ``Table~\ref{tab:table1}'' in a sentence.
+    \item Use ``\textbackslash ie'' command for ``\ie'' and use ``\textbackslash eg'' for ``\eg.''.
+    \item When referring to a table, always use ``Table~\ref{tab:table1}'' in the sentence:\\
+        \wrong{Our results are shown in Tab.~1.}\\
+        \correct{Our results are shown in Table~1.}
+
     \item The table caption should be at the top of the table.
-    \item When referring to a figure, use ``Figure~\ref{fig:figure1}'' at the beginning, and ``Fig.~\ref{fig:figure1}'' at the middle or the end of a sentence.
+    \item When referring to a figure, use ``Figure~\ref{fig:figure1}'' at the beginning of a sentence and ``Fig.~\ref{fig:figure1}'' elsewhere.\\
+        \wrong{Fig.1 shows our results.}\\
+        \correct{Our results are shown in Fig.~1.}\\
+        \correct{Figure~1 shows our results.}
     \item The figure caption should be at the bottom of the table.
@@
 \clearpage
+
 \section{Examples for the Tables}
 
-% single column
+%\subsection{Examples for the Single-column Tables}
 \input{tables/table1} % simple table
@@
 \input{tables/table5} % multi-column with bold font
-\newpage
 \input{tables/table6} % multi-column with parallel lines
@@
 
-% two column
+%\subsection{Examples for the Two-column Tables}
 \input{tables/table8} % two-column table
@@
 \input{tables/table7} % two-column table with two sub-tables
+\input{tables/table13} % two-column table with cmidrule
 \input{tables/table_figure2} % two-column tables with images in the header
 \input{tables/table10} % two tables side-by-side
-
-\clearpage
 \input{tables/table11} % table with caption at the left
-
 \input{tables/table_network1} % two column network arch table
@@
 
-\section{Examples for Figures}
-
-% Single-column
+\section{Examples for the Figures}
+%\subsection{Examples for the Single-column Figures}
 \input{figures/figure1} % single image
@@
 
-% Two column
+%\subsection{Examples for the Two-column Figures}
 \input{figures/figure7} % single image
